Appendix A: Code and supplementary figures for simulation and policy analyis

### 2018-02-01 appendix/appendixA.Rmd

---
title: "Appendix A: Code and supplementary figures for simulation and policy analyis"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
bibliography: ../manuscripts/citations.bib

---

@@

```{r library, message=FALSE}
#devtools::install_github("boettiger-lab/sarsop@0.5.0")
library(sarsop)       # Our main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)     
library(gridExtra)
```

@@

```{r S7, fig.height=10, fig.width=5}
p3 <- read_csv(file.path(log_dir, "priors.csv")) %>%
ggplot(aes(state, prior, col = policy)) + 
  geom_line(lwd=1) +
  coord_cartesian(xlim = c(0,1)) + 
  theme(legend.position = "none")

>>>>

---
title: "Appendix A: Code and supplementary figures for simulation and policy analyis"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
    keep_tex: true
bibliography: ../manuscripts/citations.bib

---
\renewcommand{\thefigure}{S\arabic{figure}}

@@

```{r library, message=FALSE,cache=FALSE}
#devtools::install_github("boettiger-lab/sarsop@0.5.0")
library(sarsop)       # Our main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)     
library(gridExtra)
```

@@

```{r S7, fig.height=10, fig.width=5, fig.cap = "policy plots, as in manuscript, figure 4. Here we include a comparison to MSY as well."}
p3 <- read_csv(file.path(log_dir, "priors.csv")) %>%
ggplot(aes(state, prior, col = policy)) + 
  geom_line(lwd=1) +
  coord_cartesian(xlim = c(0,1)) + 
  theme(legend.position = "none")
